---
title: "Additional Resources"
output: distill::distill_article
---

# Discovering Data Use and Value for Research and Policy

## Special Issue

This workshop is particularly timely as the *Harvard Data Science Review* has recently published a special issue, “Democratizing Data: Discovering Data Use for Research and Policy,” presenting cutting-edge ideas on using robust AI tools to support evidence building in public policy and science. 

```{r, echo=FALSE, results='asis'}
cat('<iframe src="https://hdsr.mitpress.mit.edu/specialissue4" width="100%" height="600px"></iframe>')
```

## Webinar
An accompanying Webinar (May 21-22, 2024) will feature authors of the papers, providing practical insights and a vision for how bottom-up collaborations and communities of practice can help shape the future of data democratization.

```{r, echo=FALSE, results='asis'}
cat('<iframe src="https://datascience.harvard.edu/calendar_event/democratizing-data-discovering-data-use-and-value-for-research-and-policy/" width="100%" height="600px"></iframe>')
```