---
title: "Day 2 - Breakout Sessions"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Attendees will be divided into groups of 6 to 7 participants with a mix of university faculty, graduate students, government employees, and private sector professionals to discuss and identify stakeholders’ needs, underutilized information, and potential improvements in evaluating and forecasting food prices. 


<span style="font-size: 20px; font-weight: bold;">**Discussion topics**</span>

<style>
  @import url('https://fonts.googleapis.com/css2?family=Public+Sans&display=swap');

  body {
    font-family: 'Public Sans', sans-serif;
  }
  
  .discussion-table {
    width: 100%;
    border-collapse: collapse;
    margin-bottom: 20px;
  }
  .discussion-table th, .discussion-table td {
    border: 1px solid #ddd;
    padding: 8px;
    text-align: left;
  }
  .discussion-table th {
    background-color: #f2f2f2;
  }
</style>

<table class="discussion-table">
  <thead>
    <tr>
      <th>Topic</th>
      <th>Discussants</th>
    </tr>
  </thead>
  <tbody>
    <tr>
      <td>Concentration and IO</td>
      <td><a href="speakers/macdonald.html" target="_blank">James MacDonald (Group 1)</a>, <a href="speakers/cakir.html" target="_blank">Metin Çakir (Group 2)</a></td>
    </tr>
    <tr>
      <td>Forecasting</td>
      <td><a href="speakers/smith.html" target="_blank">Aaron Smith (Group 3)</a>, <a href="speakers/maclachlan.html" target="_blank">Matthew MacLachlan (Group 4)</a></td>
    </tr>
    <tr>
      <td>Impacts of Price Changes</td>
      <td><a href="speakers/byrne.html" target="_blank">Anne Byrne (Group 5)</a>, <a href="speakers/okrent.html" target="_blank">Abigail Okrent (Group 6)</a></td>
    </tr>
    <tr>
      <td>Input Price Pass-Through</td>
      <td><a href="speakers/bayham.html" target="_blank">Jude Bayham (Group 7)</a>, <a href="speakers/kroetz.html" target="_blank">Kailin Kroetz (Group 8)</a></td>
    </tr>
    <tr>
      <td>International Markets</td>
      <td><a href="speakers/somogyi.html" target="_blank">Simon Somogyi (Group 9)</a>, <a href="speakers/baffes.html" target="_blank">John Baffes (Group 10)</a></td>
    </tr>
    <tr>
      <td>Price Indexes</td>
      <td><a href="speakers/zhen.html" target="_blank">Chen Zhen (Group 11)</a>, <a href="speakers/aizcorbe.html" target="_blank">Ana Aizcorbe (Group 12)</a></td>
    </tr>
  </tbody>
</table>
</div>

```{r echo=FALSE}
htmltools::HTML('
<div style="text-align: center; margin-top: 20px;">
  <a href="people.html#participants" target="_blank" style="font-size: 18px; color: blue; text-decoration: underline;">Find Your Discussion Group Here</a>
</div>
<br>
<div>
<html lang="en">
<head>
    <meta charset="UTF-8">
    <meta name="viewport" content="width=device-width, initial-scale=1.0">
    <title>Facilitation Guide</title>
    <style>
        body {
            font-family: Arial, sans-serif;
            margin: 20px;
            padding: 0;
            display: flex;
            flex-direction: column;
            align-items: center;
        }
        h2 {
            text-align: center;
        }
        iframe {
            width: 100%;
            max-width: 100%;
            height: 600px;
            border: 1px solid #ccc;
        }
        .button-container {
            margin-top: 20px;
            text-align: center;
        }
        .button {
            background-color: #007BFF;
            color: white;
            border: none;
            padding: 10px 20px;
            text-align: center;
            text-decoration: none;
            display: inline-block;
            font-size: 16px;
            margin: 4px 2px;
            cursor: pointer;
            border-radius: 4px;
        }
    </style>
</head>
<body>
    <h2>Facilitation Guide</h2>
    <iframe src="Facilitator guide_07-22-2024.pdf" width="100%" height="600px">
       Please download the PDF to view it: <a href="Facilitator guide_07-22-2024.pdf">Download PDF</a>.
    </iframe>
    <div class="button-container">
        <a href="Facilitator guide_07-22-2024.pdf" class="button" target="_blank">Open in New Window</a>
        <a href="Facilitator guide_07-22-2024.pdf" class="button" download>Download PDF</a>
    </div>
</body>
</html>
</div>
')
```


<!-- ################## -->

<div style="padding-bottom: 60px;"></div>

<!--===================================-->
<div style="text-align: center;">
  <a href="index.html" class="btn" style="background-color: black; color: white; padding: 10px 20px; text-align: center; text-decoration: none; display: inline-block;">Back to Home</a>
</div>





<!--
<span style="font-size: 20px; font-weight: bold;">**Discussion topics**</span>

| Topic  | Discussants |
|------------------------------------------|----------------------------------------------------------------------------------------|
| Concentration and IO                     | [James MacDonald](macdonald.html) (Group 1), [Metin Çakir](cakir.html) (Group 2)                      |
| Forecasting                              | [Aaron Smith](smith.html) (Group 3), [Matthew MacLachlan](maclachlan.html) (Group 4)                  |
| Impacts of Price Changes                 | [Anne Byrne](byrne.html) (Group 5), [Abigail Okrent](okrent.html) (Group 6)                        |
| Input Price Pass-Through                 | [Jude Bayham](bayham.html) (Group 7), [Kailin Kroetz](kroetz.html) (Group 8)                       |
| International Markets                    | [Simon Somogyi](somogyi.html) (Group 9), [John Baffes](baffes.html) (Group 10)                        |
| Price Indexes                            | [Chen Zhen](zhen.html) (Group 11), [Ana Aizcorbe](aizcorbe.html) (Group 12)                           |
-->
<!--

## Reflection Questions 

<span style="font-size: 20px; font-weight: bold;">**Time: 12 minutes**</span> <br>
<span style="font-size: 20px; font-weight: bold;">**Led by: Alessandro Bonanno**</span>

Each note taker, please summarize themes from your group's discussion.  

1. What features of the dashboard did you find particularly useful or surprising? (*Group 1 starts*)
2. What limitations or problems did you encounter while navigating the dashboard? (*Group 2 starts*)
3. What features would you add to the dashboard? (*Group 3 starts*)

## Final Question

<span style="font-size: 20px; font-weight: bold;">**Time: 8 minutes**</span> <br>
<span style="font-size: 20px; font-weight: bold;">**Led by: Lauren Chenarides**</span>

For the remainder of our time, we invite all participants to share their answers to the following question. Please use the "Raise Hand" feature in Zoom or write your comment in the chat.

4. Would you use this tool in your own research? Why or why not? (*Open discussion*)

-->

<!--===================================-->
<!--

<div style="text-align: center;">
  <a href="close.html" class="btn" style="background-color: black; color: white; padding: 10px 20px; text-align: center; text-decoration: none; display: inline-block;">Go to Concluding Remarks</a>
</div>


-->