---
title: "Day 2 - Breakout Sessions"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Attendees will be divided into groups of 6 to 7 participants with a mix of university faculty, graduate students, government employees, and private sector professionals to discuss and identify stakeholders’ needs, underutilized information, and potential improvements in evaluating and forecasting food prices. 

<!--
<span style="font-size: 20px; font-weight: bold;">**Discussion topics**</span>

| Topic  | Discussants |
|------------------------------------------|-----------------------------------------------------------------------------------|
| Concentration and IO                     | [James MacDonald](macdonald.html), [Metin Çakir](cakir.html)                      |
| Forecasting                              | [Aaron Smith](smith.html), [Matthew MacLachlan](maclachlan.html)                   |
| Impacts of Price Changes                 | [Anne Byrne](byrne.html), [Abigail Okrent](okrent.html)                        |
| Input Price Pass-Through                 | [Jude Bayham](bayham.html), [Kailin Kroetz](kroetz.html)                        |
| International Markets                    | [Simon Somogyi](somogyi.html), [John Baffes](baffes.html)                        |
| Price Indexes                            | [Chen Zhen](zhen.html), [Ana Aizcorbe](aizcorbe.html)                           |
-->

<span style="font-size: 20px; font-weight: bold;">**Discussion topics**</span>

<style>
  .discussion-table {
    width: 100%;
    border-collapse: collapse;
    margin-bottom: 20px;
  }
  .discussion-table th, .discussion-table td {
    border: 1px solid #ddd;
    padding: 8px;
    text-align: left;
  }
  .discussion-table th {
    background-color: #f2f2f2;
  }
</style>

<table class="discussion-table">
  <thead>
    <tr>
      <th>Topic</th>
      <th>Discussants</th>
    </tr>
  </thead>
  <tbody>
    <tr>
      <td>Concentration and IO</td>
      <td><a href="speaker/macdonald.Rmd" target="_blank">James MacDonald</a>, <a href="speaker/cakir.Rmd" target="_blank">Metin Çakir</a></td>
    </tr>
    <tr>
      <td>Forecasting</td>
      <td><a href="speaker/smith.Rmd" target="_blank">Aaron Smith</a>, <a href="speaker/maclachlan.Rmd" target="_blank">Matthew MacLachlan</a></td>
    </tr>
    <tr>
      <td>Impacts of Price Changes</td>
      <td><a href="speaker/byrne.Rmd" target="_blank">Anne Byrne</a>, <a href="speaker/okrent.Rmd" target="_blank">Abigail Okrent</a></td>
    </tr>
    <tr>
      <td>Input Price Pass-Through</td>
      <td><a href="speaker/bayham.Rmd" target="_blank">Jude Bayham</a>, <a href="speaker/kroetz.Rmd" target="_blank">Kailin Kroetz</a></td>
    </tr>
    <tr>
      <td>International Markets</td>
      <td><a href="speaker/somogyi.Rmd" target="_blank">Simon Somogyi</a>, <a href="speaker/baffes.Rmd" target="_blank">John Baffes</a></td>
    </tr>
    <tr>
      <td>Price Indexes</td>
      <td><a href="speaker/zhen.Rmd" target="_blank">Chen Zhen</a>, <a href="speaker/aizcorbe.Rmd" target="_blank">Ana Aizcorbe</a></td>
    </tr>
  </tbody>
</table>
</div>


```{r echo=FALSE}
htmltools::HTML('
<div style="text-align: center; margin-top: 20px;">
  <a href="people.html#participants" target="_blank" style="font-size: 18px; color: blue; text-decoration: underline;">Find Your Discussion Group Here</a>
</div>
')
```

<!-- ################## -->

<div style="padding-bottom: 60px;"></div>

<!--===================================-->
<div style="text-align: center;">
  <a href="index.html" class="btn" style="background-color: black; color: white; padding: 10px 20px; text-align: center; text-decoration: none; display: inline-block;">Back to Home</a>
</div>






<!--

## Reflection Questions 

<span style="font-size: 20px; font-weight: bold;">**Time: 12 minutes**</span> <br>
<span style="font-size: 20px; font-weight: bold;">**Led by: Alessandro Bonanno**</span>

Each note taker, please summarize themes from your group's discussion.  

1. What features of the dashboard did you find particularly useful or surprising? (*Group 1 starts*)
2. What limitations or problems did you encounter while navigating the dashboard? (*Group 2 starts*)
3. What features would you add to the dashboard? (*Group 3 starts*)

## Final Question

<span style="font-size: 20px; font-weight: bold;">**Time: 8 minutes**</span> <br>
<span style="font-size: 20px; font-weight: bold;">**Led by: Lauren Chenarides**</span>

For the remainder of our time, we invite all participants to share their answers to the following question. Please use the "Raise Hand" feature in Zoom or write your comment in the chat.

4. Would you use this tool in your own research? Why or why not? (*Open discussion*)

-->

<!--===================================-->
<!--

<div style="text-align: center;">
  <a href="close.html" class="btn" style="background-color: black; color: white; padding: 10px 20px; text-align: center; text-decoration: none; display: inline-block;">Go to Concluding Remarks</a>
</div>


-->